% !Mode:: "TeX:UTF-8"

\begin{Eabstract}{Lucene}{Struts 2}{Mybatis}{Apache Commons Net}{FTP searching engine}
The rapid development of the campus network construction today, most schools set up FTP servers to provide a lot of digital resources for the teachers and students, but it often cost a lot of time to find the specified resource from a large number of digital resources. Therefore design a high performance FTP searching engine to help users more quickly and more convenient get the required digital resources is necessary, and it have a positive significance to save costs of query , improve work efficiency .

This paper discusses on the development background and current research status of FTP searching engine, and introduces related technology of system implementation, mainly including Lucene, Struts 2, Apache Commons Net, Mybatis, and discussed the core principles of technology, mechanism. And describe the development process and method of FTP searching engine in detail. First, the paper analysis the function demands and performance demands of the FTP searching engine. And then based on the needs analysis, design a FTP searching engine based on B/S structure, which offers a variety of inquiry mode and fast response.

In system design stage, we point out the main module of FTP searching engine. It consists of four main modules, namely the data acquisition module, data index module, data search module and file information contrast module, and introduced the interaction between each module. In the detailed design stage, paper shows the relevant data structure and realization of each module.
\end{Eabstract}
